Building a continuous benchmarking ecosystem in bioinformatics

### 2025-02-10 review_cycle_1/highlighted_manifesto_main.tex
Add new figure

\begin{figure}
    \centering
    %\includegraphics[width=0.8\linewidth]{figures/fig_benchmarking.pdf}
    {\color{red} \caption[Definitions.]{Benchmarks, workflows and benchmarking systems capabilities.}\label{fig:definitions}}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/fig_benchmarking.pdf}
    {\color{red} \caption[Run types, properties, capabilities and features.]{Solo- and community-benchmarks, workflows, and benchmarking system-enabled (\textit{bs}) benchmarks differ in run properties and their consequences in terms of capabilities and features, including whether: inputs, truths, hidden truths, metrics or run results are available for readers; code is free software, software environments are managed, and execution automated; there is a clear track of (human) contributors; results are run in comparable hardware; an entrypoint to results or result interpretation are provided. These run intrinsic properties have consequences in terms of features (i.e. transparency, forkability, availability for metaanalysis) and technical capabilities (i.e. software versioning or ability to run anonymously and locally (stealth mode). \label{fig:definitions}}
\end{figure}
